Software

### 2023-08-16 software.qmd
update link

## `stpphawkes`
I'm the lead author of the `stpphawkes` R package ([GitHub](https://github.com/sandialabs/stpphawkes)).

>>>>

## `stpphawkes`
I'm the lead author of the `stpphawkes` R package ([CRAN](https://cran.r-project.org/web/packages/stpphawkes/index.html);[GitHub](https://github.com/sandialabs/stpphawkes)).
